\LARGE \bf Object Detection Based Behaviour with YOLO on Thymio

### 2018-05-31 paper/paper.tex
changes in the paper

@@

\author{Francesco Saverio Zuppichini$^{1}$ and Alessia Ruggeri$^{2}$% <-this % stops a space
\thanks{$^{1}$H. Kwakernaak is with Faculty of Electrical Engineering, Mathematics and Computer Science,
        University of Twente, 7500 AE Enschede, The Netherlands
        {\tt\small h.kwakernaak at papercept.net}}%
\thanks{$^{2}$P. Misra is with the Department of Electrical Engineering, Wright State University,
        Dayton, OH 45435, USA
        {\tt\small p.misra at ieee.org}}%
}

@@

\section{Architecture}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{YOLO: REAL-TIME OBJECT DETECTION}

YOLO is a trained model for real-time object detection. While prior work on object detection repurposes classifiers to perform detection, YOLO handle the object detection as a regression problem to spatially separated bounding boxes and associated class probabilities. YOLO avoids resorting to complex pipelines that are slow and hard to optimize; instead, it uses a single convolutional neural network that simultaneously predicts multiple bounding boxes and class probabilities for those boxes. Using YOLO, You Only Look Once at an image to predict what objects are present and where they are.

@@

For our project, we used the third version of YOLO, or YOLOv3, which has been improved by making it a little bigger than before, but more accurate.

@@

\begin{thebibliography}{99}
%%%%% Our bibliography
\bibitem{c1} Y. Redmon, S. Divvala, R. Girshick, and A. Farhadi, ÒYou Only Look Once: Unified, Real-Time Object Detection,Ó University of Washington, Allen Institute for AI, Facebook AI Research, May 2016, http://pjreddie.com/yolo/.
\bibitem{c2} Y. Redmon, and A. Farhadi, ÒYOLOv3: An Incremental Improvement,Ó University of Washington, Apr 2018.

>>>>

\usepackage{biblatex}
\bibliography{paper}

@@

\author{Francesco Saverio Zuppichini$^{1}$ and Alessia Ruggeri$^{2}$}% <-this % stops a space

@@

\section{Architecture}
Our architecture is composed by:
\begin{enumerate}
	\item A robot with a mounted camera and onboard computer with a running ROS node
	\item A web server running the Object Detection model
	\item A ROS node running on a local machine
\end{enumerate}
As robot, we used the \emph{MightyThymio} \cite{guzzi2018eaai}. A robot develop on top of the Thymio, a small mass-produced mobile usually used in primary  and secondary education. The MightyThymio has a powerful Odroid C1 on board, a 1GB quad-core ARM Linux machine, with a HD camera mounted on top. The authors also implemented a ROS node to communicate with it and open-sourced the code.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{YOLO: REAL-TIME OBJECT DETECTION}

YOLO \cite{DBLP:conf/cvpr/RedmonDGF16} is a trained model for real-time object detection. While prior work on object detection repurposes classifiers to perform detection, YOLO handle the object detection as a regression problem to spatially separated bounding boxes and associated class probabilities. YOLO avoids resorting to complex pipelines that are slow and hard to optimize; instead, it uses a single convolutional neural network that simultaneously predicts multiple bounding boxes and class probabilities for those boxes. Using YOLO, You Only Look Once at an image to predict what objects are present and where they are.

@@

For our project, we used the third version of YOLO, or YOLOv3 \cite{Yolo3}, which has been improved by making it a little bigger than before, but more accurate.

@@

\printbibliography

%\begin{thebibliography}{99}
%%%%%% Our bibliography
%\bibitem{c1} Y. Redmon, S. Divvala, R. Girshick, and A. Farhadi, ÒYou Only Look Once: Unified, Real-Time Object Detection,Ó University of Washington, Allen Institute for AI, Facebook AI Research, May 2016, http://pjreddie.com/yolo/.
%\bibitem{c2} Y. Redmon, and A. Farhadi, ÒYOLOv3: An Incremental Improvement,Ó University of Washington, Apr 2018.
%
%\bibitem{c3} Guzzi, Jérôme and Giusti, Alessandro and Di Caro, Gianni A. and Gambardella, Luca M.,Mighty Thymio for Higher-Level Robotics Education, IDSIA, 2018.
